\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Fortune Whyte} \\ \vspace{1pt}
    \small 306-510-6235 $|$ \href{mailto:greatfortunewhyte@yahoo.com}{\underline{greatfortunewhyte@yahoo.com}} $|$ 
    \href{https://linkedin.com/in/great-fortune-abiye-whyte-8a91a2280}{\underline{linkedin.com/in/great-fortune-abiye-whyte-8a91a2280}} $|$
    \href{https://github.com/FortuneWhyte}{\underline{github.com/FortuneWhyte}} $|$
    \href{https://whytedev.netlify.app}{\underline{whytedev.netlify.app}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Regina}{Regina, SK}
      {Associate Degree in Computer Science}{December 2025}
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C\#/C++, SQL, JavaScript, HTML/CSS, PHP, AJAX, MIPS} \\
     \textbf{Frameworks}{: React, Node.js, Express.js, Next.js, TensorFlow, PyTorch} \\
     \textbf{Developer Tools}{: Linux, Git, Google Cloud, Vercel, VS Code, Visual Studio}
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Charan Property Management}{Remote}
      {Software Administrator}{}
      \resumeItemListStart
        \resumeItem{Supported the development, deployment, and continuous improvement of internal software systems to streamline administrative workflows.}
        \resumeItem{Contributed to AI integration initiatives designed to enhance overall operational efficiency and automate routine tasks.}
        \resumeItem{Architected, deployed, and managed a robust properties database, ensuring secure and easily accessible real estate records.}
        \resumeItem{Designed and maintained the company website, optimizing technical performance and user experience for property listings.}
      \resumeItemListEnd

    \resumeSubheading
      {Haztech}{Regina, SK}
      {Public Service}{June 2023 -- Present}
      \resumeItemListStart
        \resumeItem{Delivered frontline emergency response and safety coordination during the 2024 Saskatchewan wildfires across multiple northern communities.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{UR Exam Planner} $|$ \emph{React, Node.js, Express.js, MySQL, Vercel}}{June 2025 -- Present}
          \resumeItemListStart
            \resumeItem{Engineered a full-stack academic scheduling platform automating exam data retrieval and structured calendar visualization for university students.}
            \resumeItem{Integrated RESTful APIs and dynamic state management to reduce manual exam lookup time by 50\% through intelligent filtering and query optimization.}
            \resumeItem{Deployed on Vercel with secure backend routing and scalable database architecture enabling real-time updates and persistent user sessions.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{CFL Match Predictor} $|$ \emph{React, Next.js, Python, TensorFlow, PostgreSQL, REST APIs}}{2025 -- Present}
          \resumeItemListStart
            \resumeItem{Developing a data-driven prediction platform leveraging historical CFL datasets, player statistics, and team performance metrics to generate probabilistic game outcome forecasts.}
            \resumeItem{Implementing supervised machine learning models and feature engineering pipelines to enhance predictive accuracy and optimize model generalization.}
            \resumeItem{Designing an interactive analytics dashboard that visualizes predictive insights, trend analyses, and real-time matchup simulations for users.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

\end{document}
